---
title: "R Notebook"
output: html_notebook
---
```{r}
library(gtools)
library(tidyverse)
source("prob.R")
library(dplyr)
library(janitor)
```

```{r}
titanic <- read_csv("data/titanic.csv")
```
```{r}
titanic %>% 
  distinct(class)

titanic_clean <- titanic %>%
  mutate(class = ifelse(class %in% c("1st", "2nd", "3rd"), "passenger", "crew"))

titanic_clean %>% 
distinct(class)

titanic_clean2 <- titanic_clean %>%
  tabyl(class, survived)

titanic_clean2 <- titanic_clean2 %>% 
  adorn_totals(where = c("row", "col"))

titanic_clean2

# Crew .76

679/890

# Passengers .62

817/1317

```

Tianic answers : Crew more probable to die.


Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
4/6
```
Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
6^3
```
Question 3.
In an experiment where we roll four dice:

how many outcomes are in the event where the total of the four dice equals 5, 6 or 7
?

34

what is the probability of this event?
0.02623457

what assumptions do we apply in answering part ii?

likelyhood of each num on die being equal

```{r}
s_four_dice <- rolldie(4)

s_four_dice %>% 
  summarise(size_of_s = n()) #1296

s_four_dice <- s_four_dice %>%
  mutate(total = rowSums(across(1:4)))

numbers_to_count <- c(5, 6, 7)

count <- sum(s_four_dice$total %in% numbers_to_count)

count


```
Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

1/120 or 0.008333333

```{r}
5*4*3*2*1 

1/120
```

