---
title: "R Notebook"
output: html_notebook
---

Question 1.
Find the weather forecast for the next three days online. Create a list of lists
in which each inner list should be labelled with the name of the day of the 
week. Each inner list should contain named elements telling you the temperature, 
chance of rain and wind speed.

```{r}
weather <- list(
                "Thursday" = list(temperature = 14, chance_of_rain_percent = 20, wind_speed_mph = 11),
                "Friday" = list(temperature = 16, chance_of_rain_percent = 10, wind_speed_mph = 8),
                "Saturday" = list(temperature = 17, chance_of_rain_percent = 10, wind_speed_mph = 10)
)

weather
```

Question 2.
Using the list you’ve just made find:

    The chance of rain tomorrow
    The wind speed on the day after tomorrow
    The temperature tomorrow.


```{r}
weather$Thursday$chance_of_rain_percent

weather$Friday$wind_speed_mph

weather$Thursday$temperature

```
Question 3.
Find a 14 day forecast online and create a matrix of the forecasts for 
temperature, where each week is one row and columns correspond to days.

You will want to give a name to the matrix you create.

```{r}
forecast <- matrix(c(16,22,21,15,16,17,18, 18,17,17,17,17,17,18), 
                           nrow = 2, ncol = 7, byrow = TRUE,
                           dimnames = list(c("Week1", "Week2"),
                                           c("Monday", "Tuesday", "Wednesday","Thursday","Friday","Saturday","Sunday")))

forecast
```
Question 4.
From the matrix you just made select:

    The third day of the second week
    The whole second week
    The first, third and fifth days in both weeks.

```{r}
forecast[2,3]
forecast[2,1:7]
forecast[, c(1, 3, 5)]
```
Question 5.

Write a function that pre-appends “The answer is:” to any character input, 
while for numeric input, it either just returns the number for numbers less 
than 10, or divides the number by 10 for numbers greater than 10. For anything 
else return “Invalid input”.

function_name <- function(argument_1, argument_2 = value){
  
  Do something with arguments
  
  return(output)
}

messed aroudn with 5 and 6 but cant ge tit right

```{r}
answer_or_divide <- function(x) {
  if (is.character(x)) {
    return(paste("The answer is: ", x))
  }

  if (is.numeric(x)) {
    if (x < 10) {
      return(x)
    } else {
      return(x / 10)
    }
  }

  return("Invalid input")
}
```

Question 6.
Write a function which checks if two vectors have the same elements.

    If they have the same elements in the same order, return “Exactly the same”
    If they have the same elements but in a different order, return “The same”
    If they don’t have the same elements, return “Different”.

```{r}
is_same_vector <- function(vector_1, vector_2) {
  if (all(vector_1 == vector_2)) {
    return("Exactly the same")
  }

  if (all(sort(vector_1) == sort(vector_2))) {
    return("The same")
  }

  return("Different")
}
```

